\documentclass[ ../main.tex]{subfiles}
\providecommand{\mainx}{..}
\begin{document}
\section{Introduction}
% the queries may also be rate distorted. or approximate.

%The (approximate) logical functions $\land \colon \Bool^{\fnrate}_{\fprate} \times \Bool^{\fnrate}_{\fprate} \mapsto \Bool^{\fnrate}_{\fprate}$ and $\neg \colon \Bool^{\fnrate}_{\fprate} \mapsto \Bool^{\fnrate}_{\fprate}$ are also random, e.g., assuming $\neg$ does not introduce an \emph{independent} source of error, $\neg \True^{\fnrate}$ and $\neg \False^{\fprate}$ are respectively distributed as $\False^{\fnrate}$ and $\True^{\tprate}$.

An \emph{approximate set} is a set that approximates another set of objective interest.
It is \emph{approximate} because with respect to the objective set, there are two types of errors, \emph{false positives} and \emph{false negatives}.
The \emph{Bloom filter} is a popular example of a data structure that models \emph{positive random approximate sets} with \emph{false positives} due to \emph{rate distortion}.

In \cref{sec:setalgebra}, we define the algebra of sets.

In \cref{sec:asets}, we provide a formal definition of the \emph{random approximate set} model, in which the false positive and false negative rates are \emph{expectations}.
We describe the axioms of the random approximate set model such that, if satisfied, also satisfy the axioms of the approximate algebra of sets.
We further derive the probability distribution of random approximate sets entailed by the axioms.

In \cref{sec:characteristics}, we derive the rate-distortion random variables that are fundamental to the approximate set model, such as the false positive rate.

In \cref{sec:func_rand_asets}, we provide a detailed treatment on distributions that are induced by functions that depend on random approximate sets, e.g., in \cref{sec:set_theory} we derive the probability distribution of random approximate sets that are generated from arbitrary set-theoretic operations on random approximate sets and in \cref{sec:perf} we derive several well-known binary classification performance measures of random approximate sets as a function of their error rates, such as \emph{positive predictive value}.

In \cref{sec:intervals}, we provide the probabilistic model for random approximate sets with \emph{uncertain} rate distortions, such as an uncertain false positive rate.

In \cref{sec:adt}, we provide a treatment on the random approximate set model as an abstract data type and show how that, if the generative algorithm of an approximate set model is deterministic, the random approximate set model quantifies our ignorance or uncertainty.

Finally, in \cref{sec:bool_search}, we consider Encrypted Search with secure indexes based on random approximate sets.
To prove various properties of this model, such as expected precision, we only need to show that the \emph{result sets} are approximate sets of the \emph{objective} results and all the results immediately follow.
\end{document}