\nomenclature{$\vec{x}$}{Vectors are denoted in boldface font. The \jth component of $\vec{x}$ is denoted by $x_j$.}

\nomenclature[S]{$\Set{S}$}{Sets are normally notated like this.}
\nomenclature[S]{$\RealSet$}{The set of reals $(-\infty,\infty)$.}
\nomenclature[S]{$\NatSet$}{The set of natural numbers $\{0,1\}$.}
\nomenclature[S]{$\BitSet$}{The binary set $\{0,1\}$.}
\nomenclature[S]{$\Set{A}_{p}$}{The set $\SetBuilder{a \in \Set{A}}{\operatorname{p}(a)}$ where $\operatorname{p} \colon \Set{U} \mapsto \{0,1}$ is a predicate function over some universal set.}

\nomenclature[R]{$\ASet{A}$}{A \emph{random approximate set} of $\Set{A}$ where the false positive and negative rates are unspecified.}
%\nomenclature[R]{$\ASet{A}[\tprate][\fprate]$}{A \emph{random approximate set} of $\Set{A}$ where the parameterizations are $\tprate$ and $\fprate$.}
\nomenclature[R]{$\ASet{A}[\fnrate][\fprate]$}{A \emph{random approximate set} of $\Set{A}$ where the parameterizations are $\fnrate$ and $\fprate$.}
%\nomenclature[R]{$\ASet{A}[\tprate][+]$}{A \emph{random approximate set} of $\Set{A}$ where the false positive rate is unspecified or implicit.}
\nomenclature[R]{$\ASet{A}[\fnrate][+]$}{A \emph{random approximate set} of $\Set{A}$ where the false positive rate is unspecified.}
\nomenclature[R]{$\ASet{A}[-][\fprate]$}{A \emph{random approximate set} of $\Set{A}$ where the true positive rate is unspecified.}
\nomenclature[R]{$\ASet{A}[-][\tnrate]$}{A \emph{random approximate set} of $\Set{A}$ where the false negative rate is unspecified.}
\nomenclature[R]{$\PASet{A}$}{A \emph{positive} random approximate set of $\Set{A}$ where the false positive rate is unspecified.}
\nomenclature[R]{$\PASet{A}[\fprate]$}{A \emph{positive} random approximate set of $\Set{A}$ where the false positive rate is $\fprate$.}
\nomenclature[R]{$\NASet{A}$}{A \emph{negative} random approximate set of $\Set{A}$ where the true positive rate is unspecified.}
%\nomenclature[R]{$\NASet{A}[\tprate]$}{A \emph{negative} random approximate set of $\Set{A}$ where the true positive rate is $\tprate$.}
\nomenclature[R]{$\NASet{A}[\fnrate]$}{A \emph{negative} random approximate set of $\Set{A}$ where the false negative rate is $\fnrate$.}

\nomenclature[R]{$\fprate$}{By convention, an \emph{expected} false positive rate if nothing about it is known.}
\nomenclature[R]{$\tprate$}{By convention, an \emph{expected} true positive rate if nothing about it is known.}
\nomenclature[R]{$\tnrate$}{By convention, an \emph{expected} true negative rate if nothing about it is known.}
\nomenclature[R]{$\fnrate$}{By convention, an \emph{expected} false negative rate if nothing about it is known.}

\nomenclature[R]{$\fprateob$}{By convention, an \emph{observed} false positive rate if nothing about it is known.}
\nomenclature[R]{$\tprateob$}{By convention, an \emph{observed} true positive rate if nothing about it is known.}
\nomenclature[R]{$\tnrateob$}{By convention, an \emph{observed} true negative rate if nothing about it is known.}
\nomenclature[R]{$\fnrateob$}{By convention, an \emph{observed} false negative rate if nothing about it is known.}

\nomenclature[T]{$\Card{\Set{A}}$}{The cardinality of a set $\Set{A}$.}
\nomenclature[T]{$\Set{A} \times \Set{B}$}{The Cartesian product of $\Set{A}$ and $\Set{B}$ defined as $\SetBuilder{\Pair{a}{b}}{a \in \Set{A} \land b \in \Set{B}}$.}
\nomenclature[T]{$\Set{B}^n$}{The Cartesian product $\Set{B} \times \cdots \times \Set{B}$, $n$ times.}
\nomenclature[T]{$\SetIndicator{}$}{The indicator function, $\SetIndicator{\Set{A}} \colon \Set{X} \mapsto \{0,1\}$ is defined by $\SetIndicator{\Set{A}}(x) = 1$ if $x \in \Set{A}$ and otherwise equals $0$.}
\nomenclature[T]{$\PowerSet(A)$}{The power set of $\Set{A}$.}
\nomenclature[T]{$\PS{A}$}{The power set of $\Set{A}$.}
\nomenclature[T]{$\SetUnion[\Set{A}][\Set{B}]$}{The union of $\Set{A}$ and $\Set{B}$.}
\nomenclature[T]{$\SetUnion[\ASet{A}][\ASet{B}]$}{The union of random approximate sets $\ASet{A}$ and $\ASet{B}$.}

\nomenclature[P]{$\PDF[\RV{X}]$}{The probability mass or density function of random variable $\RV{X}$.}
\nomenclature[P]{$\CDF[\RV{X}]$}{The cumulative distribution function of random variable $\RV{X}$.}

\nomenclature{$\BL$}{The bit length function.}
\nomenclature{$\RE$}{The relative efficiency function.}
\nomenclature{$\AbsoluteEfficiency$}{The absolute efficiency function.}

