\newglossaryentry{gls-set}
{
    name={set},
    description={An unordered collection of distinct elements from a universe of elements.}
}

\newglossaryentry{gls-finiteset}
{
    name={finite set},
    description={A finite collection of distinct elements from a universe of elements.}
}

\newglossaryentry{gls-preimageres}
{
    name={pre-image resistant},
    description={is when, given a hash function and a hash value, it is difficult to find an input for the given hash function that outputs the given hash value.}
}

\newglossaryentry{gls-preimageattack}
{
    name={pre-image attack},
    description={Given a hash function and a hash value, one tries to find an input for the given hash function that outputs the given hash value.}
}

\newglossaryentry{gls-randomoracle}
{
    name={random oracle},
    description={A theoretical function that maps every unique input from its domain to a uniform and random output in its range.}
}

\newglossaryentry{gls-approxset}
{
    name={approximate set},
    description={A set that approximates another set.}
}

\newglossaryentry{gls-approxfuzzyset}
{
    name={fuzzy approximate set},
    description={A fuzzy set that approximates another fuzzy set.}
}

\newglossaryentry{gls-ph}
{
    name={perfect hash function},
    description={A hash function that guarantees no collisions among members of a specified set.}
}

\newglossaryentry{gls-phf}
{
    name={Perfect Hash Filter},
    description={A data structure that implements the approximate set abstract data type.}
}

\newglossaryentry{gls-blf}
{
    name={Bloom filter},
    description={A data structure that implements the approximate set abstract data type.}
}

\newglossaryentry{gls-booleanquery}
{
    name={Boolean query},
    description={description here},
    plural={Boolean queries}
}

\newglossaryentry{gls-fprate}
{
    name={false positive rate},
    description={Given a set $\St$ and a an element $x$ that is not a member of a $\St$, an approximate set of $\St$ has $x$ with a probability denoted the \emph{false positive rate}}.
}

\newglossaryentry{gls-fnrate}
{
    name={false negative rate},
    description={Given a set $\St$ and a an element $x$ that is a member of a $\St$, an approximate set of $\St$ does not have $x$ with a probability denoted the \emph{false negative rate}}.
}

\newglossaryentry{gls-nb}
{
    name={negative binomial distribution},
    description={A distribution where we are interested in observing the number of Bernoulli trials needed to observe a specific number of ``successes.''}
}

\newacronym{nb}{NB}{negative binomial distribution}
\newacronym{geo}{GEO}{geometric distribution}
\newacronym{mle}{MLE}{maximum likelihood estimation}
\newacronym{bnf}{BNF}{Backus-Naur form}
\newacronym{IR}{IR}{information retrieval}
\newacronym{abf}{BF}{\gls{blf}}
\newacronym{aphf}{PHF}{\gls{phf}}
\newacronym{aph}{PH}{\Gls{pf}}
