\newglossaryentry{gls-preimageres}
{
    name={pre-image resistant},
    description={Given a hash function and a hash, it is difficult to find an input for the given hash function that outputs the given hash.}
}

\newglossaryentry{gls-fprate}
{
    name={false positive rate},
    description={Given a set $\St$ and a an element $x$ that is not a member of a $\St$, an approximate set of $\St$ contains $x$ with a probability denoted the \emph{false positive rate}}.
}

\newglossaryentry{gls-preimageattack}
{
    name={pre-image attack},
    description={Given a hash function and a hash, searching for an input for the given hash function that outputs the given hash.}
}

\newglossaryentry{gls-randomoracle}
{
    name={random oracle},
    description={A theoretical function that maps every unique input from its domain to a uniform and random output in its range.}
}

\newglossaryentry{gls-approxset}
{
    name={approximate set},
    description={A set $\Sp$ is an approximate set of $\St$ if $\Sp \supset \St$ and an element not in $\St$ is in $\Sp$ with a probability denoted the \gls*{gls-fprate}.}
}

\newglossaryentry{gls-shs}
{
    name={Singular Hash Set},
    description={A theoretically optimal data structure for implementing the \emph{approximate set} abstract data type.}
}

\newglossaryentry{gls-shmap}
{
    name={Singular Hash Map},
    description={A theoretically optimal data structure for implementing the \emph{approximate map} abstract data type.}
}

\newglossaryentry{gls-pf}
{
    name={perfect hash function},
    description={A hash function that guarantees no collisions among members of a specified set.}
}

\newglossaryentry{gls-phf}
{
    name={Perfect Hash Filter},
    description={A data structure for implementing the \emph{approximate set} abstract data type that is a function of a \gls*{gls-pf}.}
}

\newglossaryentry{gls-blf}
{
    name={Bloom filter},
    description={A poular data structure for implementing the \emph{approximate set} abstract data type.}
}

\newglossaryentry{gls-nb}
{
    name={negative binomial distribution},
    description={A distribution where we are interested in observing the number of Bernoulli trials needed to observe a specific number of ``successes.''}
}

\newglossaryentry{gls-geo}
{
    name={geometric distribution},
    description={A distribution where we are interested in observing the number of Bernoulli trials needed to observe a a ``successes.''}
}

\newglossaryentry{gls-set}
{
    name={set},
    description={An ordered collection of distinct elements.}
}

\newglossaryentry{gls-es}
{
    name={Encrypted Search},
    description={description here.}
}


\newacronym{acr-nb}{NB}{\gls*{gls-nb}}
\newacronym{acr-geo}{GEO}{\gls*{gls-geo}}
\newacronym{acr-shs}{SHS}{\gls*{gls-shs}}
\newacronym{acr-abf}{BF}{\gls*{gls-blf}}
\newacronym{acr-aphf}{PHF}{\gls*{gls-phf}}
\newacronym{acr-aph}{PH}{\Gls*{gls-pf}}
